### 2019-05-29 courses/tspl/2018/Instructions.tex
Setup courses/ folder.

\item
  To download the exam paper, open a terminal window and type:
  \begin{center}
    \texttt{getpapers}
  \end{center}
  This will create a subdirectory \texttt{tspl-pe} in your home directory,
  containing the following files.
  \begin{center}
    \begin{tabular}{ll}
      \texttt{tspl-pe/papers/exam.pdf}                & the exam \\
      \texttt{tspl-pe/papers/instructions.pdf}        & these instructions \\
      \texttt{tspl-pe/templates/Exam.lagda}           & exam template to edit \\
      \texttt{tspl-pe/original\_templates/Exam.lagda} & backup of exam template
    \end{tabular}
  \end{center}
  The directories \texttt{tspl-pe/papers}, \texttt{tspl-pe/original\_templates}
  are read only, but you may read and write \texttt{tspl-pe/templates}.

\item
  To setup the Agda environment, open a second terminal window and type:
  and type:
  \begin{center}
    \texttt{tspl-setup}
  \end{center}
  This will open a browser, with three tabs which contain the textbook
  \emph{Programming Language Foundations in Agda}, the documentation for the
  Agda standard library, and the documentation for Agda.  (The browser may
  also attempt to link to the internet, which brings up a tab labeled
  ``Problem loading page''; this is expected and not a problem.)

>>>>

\item
  To download the exam paper, open a terminal window and type:
  \begin{center}
    \texttt{getpapers}
  \end{center}
  This will create a subdirectory \texttt{tspl-pe} in your home directory,
  containing the following files.
  \begin{center}
    \begin{tabular}{ll}
      \texttt{tspl-pe/papers/exam.pdf}                & the exam \\
      \texttt{tspl-pe/papers/instructions.pdf}        & these instructions \\
      \texttt{tspl-pe/templates/Exam.lagda}           & exam template to edit \\
      \texttt{tspl-pe/original\_templates/Exam.lagda} & backup of exam template
    \end{tabular}
  \end{center}
  The directories \texttt{tspl-pe/papers} and
  \texttt{tspl-pe/original\_templates}
  are read only, but you may read and write \texttt{tspl-pe/templates}.

\item
  To setup the Agda environment, open a second terminal window and type:
  \begin{center}
    \texttt{tspl-setup}
  \end{center}
  This will open a browser, with three tabs which contain the textbook
  \emph{Programming Language Foundations in Agda}, the documentation for the
  Agda standard library, and the documentation for Agda.  (The browser may
  also attempt to link to the internet, which brings up a tab labeled
  ``Problem loading page''; this is expected and not a problem.)
